The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
use forest not closed

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador
Wildlife Division. Available landcover classification included nine habitat
types at 30 x 30m resolution. We distilled the landcover types into three broad
categories: foraging habitat, open habitat, and closed habitat. Foraging habitat
consisted of lichen habitat, open habitat consisted of wetland, rocky barrens,
and anthropogenic habitat types, while closed habitat consisted of coniferous
forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
Water habitat was excluded from all subsequent analyses.

@@

We generated seasonal multilayer social networks consisting of habitat-specific
monolayers. Each layer was the social association network generated in one of
three habitat types (lichen, open, and closed). For habitat-specific networks,
all GPS relocations were assigned to the corresponding habitat type and
proximity-based social network layers were generated using the R package spatsoc
(Robitaille et al. 2019) in *R version* (R Core Team 2020).

>>>>

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador
Wildlife Division. Available landcover classification included nine habitat
types at 30 x 30m resolution. We distilled the landcover types into three broad
categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
consisted of lichen habitat, open habitat consisted of wetland, rocky barrens,
and anthropogenic habitat types, while forest habitat consisted of coniferous
forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
Water habitat was excluded from all subsequent analyses.

@@

We generated seasonal multilayer social networks consisting of habitat-specific
monolayers. Each layer was the social association network generated in one of
three habitat types (lichen, open, and forest). For habitat-specific networks,
all GPS relocations were assigned to the corresponding habitat type and
proximity-based social network layers were generated using the R package spatsoc
(Robitaille et al. 2019) in *R version* (R Core Team 2020).
